Comparing and combining network-guided biomarker discovery to discover genetic susceptibility mechanisms to breast cancer on the GENESIS study

### 2020-08-20 manuscript/plos/manuscript_plos.tex
commit before moving to plos template

\title{Combining network-guided GWAS to discover susceptibility mechanisms for breast cancer}
\author{Héctor Climente-González$^{1,2,3,4,\spadesuit}$, Christine Lonjou$^{1,2,3}$, Fabienne Lesueur$^{1,2,3}$, \\
GENESIS Study collaborators$^{1,2,3}$, Dominique Stoppa-Lyonnet$^{5,6,7}$, \\
Nadine Andrieu$^{1,2,3}$, Chloé-Agathe Azencott$^{3,1,2}$}
\date{\small{
  \raggedright{
  $^{1}$Institut Curie, PSL Research University, F-75005 Paris, France;\\
  $^{2}$INSERM, U900, F-75005 Paris, France;\\
  $^{3}$MINES ParisTech, PSL Research University, CBIO-Centre for Computational Biology, F-75006 Paris, France;\\
  $^{4}$RIKEN Center for Advanced Intelligence Project (AIP), Tokyo, 103-0027, Japan; \\
  $^{5}$Service de Génétique, Institut Curie, F-75005 Paris, France;\\
  $^{6}$INSERM, U830, F-75005 Paris, France;\\
  $^{7}$Université Paris Descartes.\\
  }
  \raggedright{$^{\spadesuit}$Corresponding author: \href{hector.climente@riken.jp}{hector.climente@riken.jp}\\}
}
}
\hypersetup{
  pdfauthor={Héctor Climente-González, Christine Lonjou, Fabienne Lesueur, GENESIS Study collaborators, Dominique Stoppa-Lyonnet, Nadine Andrieu, Chloé-Agathe Azencott},
  pdftitle={Combining network-guided GWAS to discover susceptibility mechanisms for breast cancer},
  pdfkeywords={},
  pdfsubject={},
  pdflang={English}}
\begin{document}

@@

\begin{abstract}
Systems biology provides a comprehensive approach to biomarker discovery and biological hypothesis building. Indeed, it allows to jointly consider the statistical association between gene variation and a phenotype, and the biological context of each gene, represented as a network. In this work, we study six network methods which identify subnetworks with high association scores to a phenotype. Specifically, we examine their utility to discover new biomarkers for breast cancer susceptibility by interrogating a genome-wide association study (GWAS) focused on French women with a family history of breast cancer and tested negative for pathogenic variants in \emph{BRCA1} and \emph{BRCA2}. We perform an in-depth benchmarking of the methods with regards to size of the solution subnetwork, their utility as biomarkers, and the stability and the runtime of the methods. By trading statistical stringency for biological meaningfulness, most network methods give more compelling results than standard SNP- and gene-level analyses, recovering causal subnetworks tightly related to cancer susceptibility. For instance, we show a general alteration of the neighborhood of \emph{COPS5}, a gene related to multiple hallmarks of cancer. Importantly, we find a significantly large overlap between the genes in the solution networks and the genes significantly associated in the largest GWAS on susceptibility to breast cancer. Yet, network methods are notably unstable, producing different results when the input data changes slightly. To account for that, we produce a stable consensus subnetwork, formed by the most consistently selected genes. The stable consensus is composed of 68 genes, enriched in known breast cancer susceptibility genes (\emph{BLM}, \emph{CASP8}, \emph{CASP10}, \emph{DNAJC1}, \emph{FGFR2}, \emph{MRPS30}, and \emph{SLC4A7}, Fisher's exact test P\=/value~=~$3 \times 10^{-4}$) and occupying more central positions in the network than average. The network seems organized around \emph{CUL3}, encoding an ubiquitin ligase related protein that regulates the protein levels of several genes involved in cancer progression. In conclusion, this article shows the pertinence of network-based analyses to tackle known issues with GWAS, namely lack of statistical power and of interpretable solutions. Project-agnostic implementations of each of the network methods are available at \url{https://github.com/hclimente/gwas-tools} to facilitate their application to other GWAS datasets.
\end{abstract}

@@

\section{Methods}
\subsection{GENESIS}

\paragraph{SNP networks}
SConES \cite{azencott_efficient_2013} is the only network method designed to handle SNP networks. As in gene networks, two SNPs are connected in a SNP network when there is evidence of shared functionality between two SNPs. \citet{azencott_efficient_2013} proposed three ways of building these networks: connecting the SNPs consecutive in the genomic sequence (``GS network''); interconnecting all the SNPs mapped to the same gene, on top of GS (``GM network''); and interconnecting all SNPs mapped to two genes for which a protein-protein interaction exists, on top of GM (``GI network''). We focused on the GI network, as it fits the scope of this work better, using the PPIN described above. However, at different stages of this work we also used GS and GM for comparison. For the GM network, we used the mapping described in Section~\ref{methods:node_score}. In all three the node scores are the association scores of the individual SNPs with the phenotype (1~d.f.~\(\chi\)\textsuperscript{2}). The properties of these three subnetworks are available in Supplementary Table \ref{tab:snp_solutions}.

were $p(v)~=~w(v) - w'$ is the \emph{profit} of adding a node, $c(e)~=~w'$ is the \emph{cost} of adding an edge, and $w' = min_{v \in V_{G}} w(v)$ is the smallest node weight of $G$. All three are positive quantities. Heinz implements the algorithm from \citet{ljubic_algorithmic_2006} which, in practice is often fast and optimal, although neither is guaranteed. We used BioNet's implementation of heinz \cite{beisser_bionet:_2010,heinz}.

\item[{HotNet2}] HotNet2 was developed to find connected subgraphs of genes frequently mutated in cancer \cite{leiserson_pan-cancer_2015}. To that end, it considers both the local topology of the network and the scores of the nodes. The former is captured by an insulated heat diffusion process: at initialization, the score of the node determines its initial heat; iteratively each node yields heat to its ``colder'' neighbors, and receives heat from its ``hotter'' neighbors, while retaining part of its own (hence, \emph{insulated}). This process continues until equilibrium is reached, and results in a diffusion matrix $F$. $F$ is used to compute the similarity matrix $E$ that models exchanged heat as
\begin{equation*} 
E = F \operatorname{diag}(w(V)), 
\end{equation*}
where $\operatorname{diag}(w(V))$ is a diagonal matrix with the node scores in its diagonal. For any two nodes $i$ and $j$, $E_{ij}$ models the amount of heat that diffuses from node $j$ to node $i$, which can be interpreted as a (non-symmetric) similarity between those two nodes. To obtain densely connected subnetworks, HotNet2 prunes $E$, only preserving edges such that $w(E) > \delta$. Lastly, HotNet2 evaluates the statistical significance of the subnetworks by comparing their size to the size of networks obtained by permuting the node scores. We assigned initial node scores as in \citet{nakka_gene_2016}, assigning a score of 0 for the genes with low probability of being associated to the disease, and -log\textsubscript{10}(P\=/value) to those likely to be. In this dataset, the threshold separating both was a P\=/value of 0.125, which was obtained using a local FDR approach \cite{scheid_twilight;_2005}. HotNet2 has two parameters: the restart probability \(\beta\), and the threshold heat \(\delta\). Both parameters are set automatically by the algorithm, which is robust to their values \cite{leiserson_pan-cancer_2015}. HotNet2 is implemented in Python \cite{hotnet2}.

where \(\lambda\) and \(\eta\) are hyperparameters that control the sparsity and the connectivity of the model. The connectivity term penalizes disconnected solutions, with many edges between nodes that are selected and nodes that are not. Given a $\lambda$ and an $\eta$, the aforementioned problem has a unique solution, that SConES finds using a graph min-cut procedure. As in \citet{azencott_efficient_2013}, we selected \(\lambda\) and \(\eta\) by cross-validation, choosing the values that produce the most stable solution across folds. In this case, the selected hyperparameters were \(\eta\)~=~3.51, \(\lambda\)~=~210.29 for SConES GS; \(\eta\)~=~3.51, \(\lambda\)~=~97.61 for SConES GM; and \(\eta\)~=~3.51, \(\lambda\)~=~45.31 for SConES GI. We used the version on SConES implemented in the R package martini \cite{martini}.
\end{description}

We searched for pathways enriched in the gene subnetworks produced by the above methods. We conducted an hypergeometric test on pathways from Reactome \cite{Jassal2019} using the R package ReactomePA \cite{Yu2016}. The universe of genes included any gene that we could map to a SNP in the iCOGS array (Section \ref{methods:node_score}). We adjusted the P-values for multiple testing as in \citet{Benjamini1995} (BH).Pathways with an BH adjusted P\=/value \textless~0.05 were deemed significant. As the significant pathways are often overlapping and redundant, the results were manually curated afterwards.

We compared the runtime, the number of selected genes/SNPs, and the stability (sensitivity of the result to small changes in the input, here, using different \emph{train} sets) of the different network methods. The stability was quantified using the Pearson correlation to measure the overlap between different runs as suggested by \citet{nogueira_measuring_2016}.

@@

As not all databases compile the same interactions, the choice of the PPIN determines the final output. In this work we used exclusively interactions from HINT from high-throughput experiments. This responds to concerns about adding interactions identified in targeted studies and prone to a ``rich getting richer'' phenomenon: popular genes have a higher proportion of their interactions described \cite{cai_broker_2010,das_hint:_2012}, and they might bias discovery by reducing the average shortest path length between two random nodes. On the other hand, \citet{huang_systematic_2018} found that the best predictor of the performance of a network for disease gene discovery is the size of the network, which supports using the largest amount of interactions. When we compared the impact of using a larger network containing interactions from both high-throughput experiments and the literature (Section~\ref{methods:networks}), we found that for most of the methods it did not greatly change the size or the stability of the solution, the classification accuracy, or the runtime (Supplementary Figure~\ref{sfig:lc_ht_comparison}). This supports using only interactions from high-throughput experiments, which produces apparently similar solutions and avoids falling into ``circular reasonings'', where the best known genes are artificially pushed into the solutions.

@@

@@

\section*{Funding and acknowledgments}

This project was supported by funding from Agence Nationale de la Recherche (ANR-18-CE45-0021-01) and from the European Union’s Horizon 2020 research and innovation program (Marie Skłodowska-Curie [666003]). Financial support for GENESIS resource and genotyping was provided by the Ligue Nationale contre le Cancer (grants PRE05/DSL, PRE07/DSL, PRE11/NA), the French National Institute of Cancer (INCa grant b2008-029/LL-LC) and the comprehensive cancer center SiRIC (Site de Recherche Intégrée sur le Cancer: INCa-DGOS-4654).

We wish to thank Om Kulkarni for helpful discussion on gene-based GWAS and PPIN databases, and the genetic epidemiology platform (the PIGE, Plateforme d'Investigation en Génétique et Epidemiologie: S. Eon-Marchais, M. Marcou, D. Le Gal, L. Toulemonde, J. Beauvallet, N. Mebirouk, E. Cavaciuti), the biological resource centre (S. Mazoyer, F. Damiola, L. Barjhoux, C. Verny-Pierre, V. Sornin) and all the GENESIS collaborating cancer clinics clinics (Clinique Sainte Catherine, Avignon: H. Dreyfus; Hôpital Saint Jacques, Besançon: M-A. Collonge-Rame; Institut Bergonié, Bordeaux: M.Longy, A. Floquet, E. Barouk-Simonet; CHU, Brest: S. Audebert; Centre François Baclesse, Caen: P. Berthet; Hôpital Dieu, Chambéry: S. Fert-Ferrer; Centre Jean Perrin, Clermont-Ferrand: Y-J. Bignon; Hôpital Pasteur, Colmar: J-M. Limacher; Hôpital d’Enfants CHU – Centre Georges François Leclerc, Dijon: L. Faivre-Olivier; CHU, Fort de France: O. Bera; CHU Albert Michallon, Grenoble: D. Leroux; Hôpital Flaubert, Le Havre: V. Layet; Centre Oscar Lambret, Lille: P. Vennin, C. Adenis; Hôpital Jeanne de Flandre, Lille: S. Lejeune-Dumoulin, S. Manouvier-Hanu; CHRU Dupuytren, Limoges: L. Venat-Bouvet; Centre Léon Bérard, Lyon: C. Lasset, V. Bonadona; Hôpital Edouard Herriot, Lyon: S. Giraud; Institut Paoli-Calmettes, Marseille: F. Eisinger, L. Huiart; Centre Val d’Aurelle – Paul Lamarque, Montpellier: I. Coupier; CHU Arnaud de Villeneuve, Montpellier: I. Coupier, P. Pujol; Centre René Gauducheau, Nantes: C. Delnatte; Centre Catherine de Sienne, Nantes: A. Lortholary; Centre Antoine Lacassagne, Nice: M. Frénay, V. Mari; Hôpital Caremeau, Nîmes: J. Chiesa; Réseau Oncogénétique Poitou Charente, Niort: P. Gesta; Institut Curie, Paris: D. Stoppa-Lyonnet, M. Gauthier-Villars, B. Buecher, A. de Pauw, C. Abadie, M. Belotti; Hôpital Saint-Louis, Paris: O. Cohen-Haguenauer; Centre Viggo-Petersen, Paris: F. Cornélis; Hôpital Tenon, Paris: A. Fajac; GH Pitié Salpétrière et Hôpital Beaujon, Paris: C. Colas, F. Soubrier, P. Hammel, A. Fajac; Institut Jean Godinot, Reims: C. Penet, T. D. Nguyen; Polyclinique Courlancy, Reims: L. Demange, C. Penet; Centre Eugène Marquis, Rennes: C. Dugast; Centre Henri Becquerel, Rouen: A. Chevrier, T. Frebourg, J. Tinat, I. Tennevet, A. Rossi; Hôpital René Huguenin/Institut Curie, Saint Cloud: C. Noguès, L. Demange, E. Mouret-Fourme; CHU, Saint-Etienne: F. Prieur; Centre Paul Strauss, Strasbourg: J-P. Fricker, H. Schuster; Hôpital Civil, Strasbourg: O. Caron, C. Maugard; Institut Claudius Regaud, Toulouse: L. Gladieff, V. Feillel; Hôpital Bretonneau, Tours: I. Mortemousque; Centre Alexis Vautrin, Vandoeuvre-les-Nancy: E. Luporsi; Hôpital de Bravois, Vandoeuvre-les-Nancy: P. Jonveaux; Gustave Roussy, Villejuif: A. Chompret, O. Caron).

\bibliographystyle{abbrvnat}
\bibliography{bibliography}

>>>>

\title{Comparing and combining network-guided biomarker discovery to discover genetic susceptibility mechanisms to breast cancer on the GENESIS study}
\author{Héctor Climente-González$^{1,2,3,4,\spadesuit}$, Christine Lonjou$^{1,2,3}$, Fabienne Lesueur$^{1,2,3}$, \\
Dominique Stoppa-Lyonnet$^{5,6,7,\clubsuit}$, Nadine Andrieu$^{1,2,3}$, Chloé-Agathe Azencott$^{3,1,2}$}
\date{\small{
  \raggedright{
  $^{1}$Institut Curie, PSL Research University, F-75005 Paris, France;\\
  $^{2}$INSERM, U900, F-75005 Paris, France;\\
  $^{3}$MINES ParisTech, PSL Research University, CBIO-Centre for Computational Biology, F-75006 Paris, France;\\
  $^{4}$RIKEN Center for Advanced Intelligence Project (AIP), Tokyo, Japan; \\
  $^{5}$Service de Génétique, Institut Curie, F-75005 Paris, France;\\
  $^{6}$INSERM, U830, F-75005 Paris, France;\\
  $^{7}$Université Paris Descartes.\\
  $^{\clubsuit}$For the GENESIS study group\\
  $^{\spadesuit}$Corresponding author: \href{hector.climente@riken.jp}{hector.climente@riken.jp}\\
  }
  }
}
\hypersetup{
  pdfauthor={Héctor Climente-González, Christine Lonjou, Fabienne Lesueur, GENESIS Study collaborators, Dominique Stoppa-Lyonnet, Nadine Andrieu, Chloé-Agathe Azencott},
  pdftitle={Combining network-guided GWAS to discover susceptibility mechanisms for breast cancer},
  pdfkeywords={},
  pdfsubject={},
  pdflang={English}}
\begin{document}

@@

\begin{abstract}
Systems biology provides a comprehensive approach to biomarker discovery and biological hypothesis building. Indeed, it allows to jointly consider the statistical association between gene variation and a phenotype, and the biological context of each gene, represented as a network. In this work, we study six network methods which identify subnetworks with high association scores to a phenotype. Specifically, we examine their utility to discover new biomarkers for breast cancer susceptibility by interrogating a genome-wide association study (GWAS) focused on French women with a family history of breast cancer and tested negative for pathogenic variants in \emph{BRCA1} and \emph{BRCA2}. We perform an in-depth benchmarking of the methods with regards to size of the solution subnetwork, their utility as biomarkers, and the stability and the runtime of the methods. By trading statistical stringency for biological meaningfulness, most network methods give more compelling results than standard SNP- and gene-level analyses, recovering causal subnetworks tightly related to cancer susceptibility. For instance, we show a general alteration of the neighborhood of \emph{COPS5}, a gene related to multiple hallmarks of cancer. Importantly, we find a significantly large overlap between the genes in the solution networks and the genes significantly associated in the largest GWAS on susceptibility to breast cancer. Yet, network methods are notably unstable, producing different results when the input data changes slightly. To account for that, we produce a stable consensus subnetwork, formed by the most consistently selected genes. The stable consensus is composed of 68 genes, enriched in known breast cancer susceptibility genes (\emph{BLM}, \emph{CASP8}, \emph{CASP10}, \emph{DNAJC1}, \emph{FGFR2}, \emph{MRPS30}, and \emph{SLC4A7}, Fisher's exact test P\=/value~=~$3 \times 10^{-4}$) and occupying more central positions in the network than average. The network seems organized around \emph{CUL3}, encoding an ubiquitin ligase related protein that regulates the protein levels of several genes involved in cancer progression. In conclusion, this article shows the pertinence of network-based analyses to tackle known issues with GWAS, namely lack of statistical power and of interpretable solutions. Project-agnostic implementations of each of the network methods are available at \url{https://github.com/hclimente/gwas-tools} to facilitate their application to other GWAS datasets.\\

\raggedright{\textbf{Author summary}}

In genome-wide association studies (GWAS), thousands of genomes are scanned to identify variants associated with a complex trait. Over the last 15 years, GWAS have advanced our understanding of the genetics of complex diseases, and in particular of hereditary cancers. Yet, they have led to an apparent paradox: the more we perform such studies, the more it seems that the entire genome is involved in every disease. An elegant explanation has been proposed with the omnigenic model: only a limited number of core genes are directly involved in the disease; but gene functions are deeply interrelated, so that many other genes are able to alter the function of the core genes. These interrelations are often modeled as networks, and multiple algorithms have been proposed to use these networks to identify the subset of core genes involved in a specific trait. In this study, we characterize six such network methods on GENESIS, a GWAS dataset for familial breast cancer in the French population. Combining these approaches allows us to identify potentially novel breast cancer susceptibility genes, and provides a mechanistic explanation for their role in the development of the disease. Our pipeline can easily be applied to other diseases.
\end{abstract}

@@

@@

As not all databases compile the same interactions, the choice of the PPIN determines the final output. In this work we used exclusively interactions from HINT from high-throughput experiments. This responds to concerns about adding interactions identified in targeted studies and prone to a ``rich getting richer'' phenomenon: popular genes have a higher proportion of their interactions described \cite{cai_broker_2010,das_hint:_2012}, and they might bias discovery by reducing the average shortest path length between two random nodes. On the other hand, Huang et al. \cite{huang_systematic_2018} found that the best predictor of the performance of a network for disease gene discovery is the size of the network, which supports using the largest amount of interactions. When we compared the impact of using a larger network containing interactions from both high-throughput experiments and the literature (Section~\ref{methods:networks}), we found that for most of the methods it did not greatly change the size or the stability of the solution, the classification accuracy, or the runtime (Supplementary Figure~\ref{sfig:lc_ht_comparison}). This supports using only interactions from high-throughput experiments, which produces apparently similar solutions and avoids falling into ``circular reasonings'', where the best known genes are artificially pushed into the solutions.

@@

\section{Materials and methods}
\subsection{GENESIS}

\paragraph{SNP networks}
SConES \cite{azencott_efficient_2013} is the only network method designed to handle SNP networks. As in gene networks, two SNPs are connected in a SNP network when there is evidence of shared functionality between two SNPs. Azencott et al. \cite{azencott_efficient_2013} proposed three ways of building these networks: connecting the SNPs consecutive in the genomic sequence (``GS network''); interconnecting all the SNPs mapped to the same gene, on top of GS (``GM network''); and interconnecting all SNPs mapped to two genes for which a protein-protein interaction exists, on top of GM (``GI network''). We focused on the GI network, as it fits the scope of this work better, using the PPIN described above. However, at different stages of this work we also used GS and GM for comparison. For the GM network, we used the mapping described in Section~\ref{methods:node_score}. In all three the node scores are the association scores of the individual SNPs with the phenotype (1~d.f.~\(\chi\)\textsuperscript{2}). The properties of these three subnetworks are available in Supplementary Table \ref{tab:snp_solutions}.

were $p(v)~=~w(v) - w'$ is the \emph{profit} of adding a node, $c(e)~=~w'$ is the \emph{cost} of adding an edge, and $w' = min_{v \in V_{G}} w(v)$ is the smallest node weight of $G$. All three are positive quantities. Heinz implements the algorithm from Ljubić et al. \cite{ljubic_algorithmic_2006} which, in practice is often fast and optimal, although neither is guaranteed. We used BioNet's implementation of heinz \cite{beisser_bionet:_2010,heinz}.

\item[{HotNet2}] HotNet2 was developed to find connected subgraphs of genes frequently mutated in cancer \cite{leiserson_pan-cancer_2015}. To that end, it considers both the local topology of the network and the scores of the nodes. The former is captured by an insulated heat diffusion process: at initialization, the score of the node determines its initial heat; iteratively each node yields heat to its ``colder'' neighbors, and receives heat from its ``hotter'' neighbors, while retaining part of its own (hence, \emph{insulated}). This process continues until equilibrium is reached, and results in a diffusion matrix $F$. $F$ is used to compute the similarity matrix $E$ that models exchanged heat as
\begin{equation*} 
E = F \operatorname{diag}(w(V)), 
\end{equation*}
where $\operatorname{diag}(w(V))$ is a diagonal matrix with the node scores in its diagonal. For any two nodes $i$ and $j$, $E_{ij}$ models the amount of heat that diffuses from node $j$ to node $i$, which can be interpreted as a (non-symmetric) similarity between those two nodes. To obtain densely connected subnetworks, HotNet2 prunes $E$, only preserving edges such that $w(E) > \delta$. Lastly, HotNet2 evaluates the statistical significance of the subnetworks by comparing their size to the size of networks obtained by permuting the node scores. We assigned initial node scores as in Nakka et al. \cite{nakka_gene_2016}, assigning a score of 0 for the genes with low probability of being associated to the disease, and -log\textsubscript{10}(P\=/value) to those likely to be. In this dataset, the threshold separating both was a P\=/value of 0.125, which was obtained using a local FDR approach \cite{scheid_twilight;_2005}. HotNet2 has two parameters: the restart probability \(\beta\), and the threshold heat \(\delta\). Both parameters are set automatically by the algorithm, which is robust to their values \cite{leiserson_pan-cancer_2015}. HotNet2 is implemented in Python \cite{hotnet2}.

where \(\lambda\) and \(\eta\) are hyperparameters that control the sparsity and the connectivity of the model. The connectivity term penalizes disconnected solutions, with many edges between nodes that are selected and nodes that are not. Given a $\lambda$ and an $\eta$, the aforementioned problem has a unique solution, that SConES finds using a graph min-cut procedure. As in Azencott et al. \cite{azencott_efficient_2013}, we selected \(\lambda\) and \(\eta\) by cross-validation, choosing the values that produce the most stable solution across folds. In this case, the selected hyperparameters were \(\eta\)~=~3.51, \(\lambda\)~=~210.29 for SConES GS; \(\eta\)~=~3.51, \(\lambda\)~=~97.61 for SConES GM; and \(\eta\)~=~3.51, \(\lambda\)~=~45.31 for SConES GI. We used the version on SConES implemented in the R package martini \cite{martini}.
\end{description}

We searched for pathways enriched in the gene subnetworks produced by the above methods. We conducted an hypergeometric test on pathways from Reactome \cite{Jassal2019} using the R package ReactomePA \cite{Yu2016}. The universe of genes included any gene that we could map to a SNP in the iCOGS array (Section \ref{methods:node_score}). We adjusted the P-values for multiple testing as in Benjamini and Hochberg \citet{Benjamini1995} (BH). Pathways with an BH adjusted P\=/value \textless~0.05 were deemed significant. As the significant pathways are often overlapping and redundant, the results were manually curated afterwards.

We compared the runtime, the number of selected genes/SNPs, and the stability (sensitivity of the result to small changes in the input, here, using different \emph{train} sets) of the different network methods. The stability was quantified using the Pearson correlation to measure the overlap between different runs as suggested by Nogueira and Brown \cite{nogueira_measuring_2016}.

@@

\section*{Acknowledgments}

We wish to thank Om Kulkarni for helpful discussion on gene-based GWAS and PPIN databases, and the genetic epidemiology platform (the PIGE, Plateforme d'Investigation en Génétique et Epidemiologie), the biological resource centre and all the GENESIS collaborating cancer clinics clinics.

\bibliographystyle{vancouver}
\bibliography{bibliography}
